% ______________________________________________________________________________
%
%   2DV610 Software Testing -- Assignment 2 Task 1
%
%   Author:  Jonas Sjöberg
%            Linnaeus University
%            js224eh@student.lnu.se
%            github.com/jonasjberg
%            www.jonasjberg.com
%
%  License:  Creative Commons Attribution 4.0 International (CC BY 4.0)
%            <http://creativecommons.org/licenses/by/4.0/legalcode>
%            See LICENSE.md for additional licensing information.
% ______________________________________________________________________________


\section{Manual Test Cases}
%
% TODO: Write manual test cases for the application.
%


% Manual Test Cases
%
% * Are the manual test-cases traceable to which requirement that is tested?
% * Do each manual test-case describe, input and expected output? (when relevant)


\subsection{Requirements}
The following requirements should be transformed into actual test cases;
\begin{enumerate}
  \item The web server should be responsive under high load.
        % Stress tests, Smoke tests.
  \item The web server must follow minimum requirements for HTTP 1.1
        % Unit tests, Integration/System tests.
  \item The web server must work on Linux, Mac, Windows*.
        % OS-specific Integration/System tests.
  \item The web server must be absolutely secure.
        % Fuzzing, Property-based tests, Penetration tests, Security Auditing.
\end{enumerate}


\subsection{Test Cases}
\subsubsection{\texttt{UC1} --- Start Server}

\begin{quote}
Primary Actor: Administrator

Postcondition: 
* A web server has been started
* A note in the access log was written, that the server was started

Main scenario
1. Starts when an administrator wants to start the server.
2. System asks for socket port number and shared resource container 
3. The administrator provides a socket port number and a shared resource container
4. System starts a web server on the given port and presents that the server was started and writes a note in the access log.

Alternate Scenarios

* 4a. The web server could not be started due to socket was taken
    1. System presents an error message: “Socket XX was taken” (XX is the socket number, Example “80”)
    2. Exit Use Case

* 4b. The web server could not be started due restriction on the shared resource container
    1. System presents an error message: “No access to folder XX” (XX is the shared resource container provided, Example “\var\www”)
    2. Exit Use Case

* 4c. The access log could not be written to
   1. System presents an error message. “Cannot write to server log file log.txt”
   2. Exit Use Case

\end{quote}
